The Heavy Photon Search Test Detector

### 2013-11-24 hps-testrun-nim.tex
small text fix
Added expected momentum resolution.
Adding new E/p plot

By selecting \ee{} pairs from the triggered events we are able to study basic distributions of pair 
production kinematics and in particular those related to our vertex performance. Pairs of opposite charge 
tracks, one in the top and one in the bottom half of the SVT, with momentum larger than 400~MeV were 
selected. The pair production kinematics are relatively well reproduced given the alignment of the 
tracker; Fig.~\ref{fig:pair_kin} shows the invariant mass and ratio of electron momentum over the sum of 
electron and positron. 
 \begin{center}
{\small
\begin{figure*}[ht]
   \includegraphics[width=5cm]{figures/h_trk_top_px_h_trk_top_px_trigsel4hit_pair1351_twotrkfilt-v6-paper}
   \includegraphics[width=5cm]{figures/h_invM_h_invM_trigsel4hit_pair1351_twotrkfilt-v6-paper}
   \includegraphics[width=5cm]{figures/h_sumE_h_sumE_trigsel4hit_pair1351_twotrkfilt-v6-paper}
\caption{Kinematic distributions for e$^+$e$^-$ pairs selected by opposite charged tracks in the top and bottom half of the tracker: track momentum in the top half of the SVT (left), invariant mass (middle) and the sum of the track momentum for the pair (right).}
\label{fig:pair_kin}
\end{figure*}
}
\end{center}
We estimate the accuracy of the SVT momentum scale and resolution by looking at the agreement 
between data and simulation in the shape of the kinematic distributions for single- and two track 
events.  By adjusting the overall momentum scale and smearing the simulated events with a 
Gaussian resolution we estimate an uncertainty of 10\% on both the momentum scale and 
resolution in the Test run. This uncertainty is

@@

The ratio of the ECal cluster energy $E$ to the momentum $p$ of a matched track in the SVT was used 
to determine the conversion factors from ADC counts to energy. To compare data and simulation, all 
inoperable or noisy channels in the SVT and ECal was disabled in both data and simulation; any 
efficiency or bias that affect the data should be reflected in the simulation. 
%Furthermore, a conversion factor calibration is performed to equalize the gains of  each channel.  simulation to those observed in data by comparing .  The ``weighted $E/p$'' for each crystal is computed, 
representing the average $E/p$ for clusters that include the crystal
% $\frac{\sum_j w_{j,i}}{\sum_j\frac{P_j}{E_j}w_{j,i}}$.
Iteratively, conversion coefficients for each module is adjusted until the $E/p$ ratio in data and 
simulation are similar. The distribution of the $E/p$ ratio in data and simulation can be seen in 
Fig.~\ref{fig:gains}. 
\begin{figure}[]
\begin{center}
{\small
	\includegraphics[width=7cm]{figures/eoverp_MC_egs_0_016x0_June5_2013_Sho_Ecal_presentation.png}
	\includegraphics[width=7cm]{figures/eoverp_data_run1351_June5_2013_Sho_Ecal_presentation.png}
	\caption{The ECal energy over track momentum ratio for simulation (top) and data (bottom).\color{red}{\bf (Update style.)}} 
	\label{fig:gains}
}
\end{center}
\end{figure}
The peak position of the distribution indicates the sampling fraction of the ECal, 
the fraction of the incident particle energy measured in the cluster. The width and tails of the distribution 
in data indicates imperfect calibration and noise of the ECal modules. This level of calibration and the 
agreement with simulation was found to be sufficient for the multiple scattering analysis using 
normalized event rates described in Sec.~\ref{sec:mcs}.

>>>>

By selecting \ee{} pairs from the triggered events we are able to study basic distributions of pair 
production kinematics and in particular those related to our vertex performance. Pairs of opposite charge 
tracks, one in the top and one in the bottom half of the SVT, with momentum larger than 400~MeV were 
selected. The pair production kinematics are relatively well reproduced given the alignment of the 
tracker; Fig.~\ref{fig:pair_kin} shows the invariant mass and ratio of electron momentum over the sum of 
electron and positron. 
 \begin{center}
{\small
\begin{figure*}[ht]
   \includegraphics[width=5cm]{figures/h_trk_top_px_h_trk_top_px_trigsel4hit_pair1351_twotrkfilt-v6-paper}
   \includegraphics[width=5cm]{figures/h_invM_h_invM_trigsel4hit_pair1351_twotrkfilt-v6-paper}
   \includegraphics[width=5cm]{figures/h_sumE_h_sumE_trigsel4hit_pair1351_twotrkfilt-v6-paper}
\caption{Kinematic distributions for e$^+$e$^-$ pairs selected by opposite charged tracks in the top and bottom half of the tracker: track momentum in the top half of the SVT (left), invariant mass (middle) and the sum of the track momentum for the pair (right).}
\label{fig:pair_kin}
\end{figure*}
}
\end{center}
We estimate the accuracy of the SVT momentum scale and resolution by looking at the agreement 
between data and simulation in the shape of the kinematic distributions for single- and two track 
events.  By adjusting the overall momentum scale and smearing the simulated events with a 
Gaussian resolution we estimate an uncertainty of 10\% on both the momentum scale and 
resolution in the Test run. The expected momentum resolution from simulation is between 4-5\% 
for tracks in the momentum range of the Test run.

@@

The ratio of the ECal cluster energy $E$ to the momentum $p$ of a matched track in the SVT was used 
to determine the conversion factors from ADC counts to energy. To compare data and simulation, all 
inoperable or noisy channels in the SVT and ECal was disabled in both data and simulation; any 
efficiency or bias that affect the data should be reflected in the simulation. 
%Furthermore, a conversion factor calibration is performed to equalize the gains of  each channel.  simulation to those observed in data by comparing .  The ``weighted $E/p$'' for each crystal is computed, 
representing the average $E/p$ for clusters that include the crystal
% $\frac{\sum_j w_{j,i}}{\sum_j\frac{P_j}{E_j}w_{j,i}}$.
Iteratively, conversion coefficients for each module is adjusted until the $E/p$ ratio in data and 
simulation are similar. The distribution of the $E/p$ ratio in data and simulation can be seen in 
Fig.~\ref{fig:gains}. 
{\small
\begin{figure}[]
\begin{center}
	\includegraphics[width=7cm]{figures/h_Ep_data_h_Ep_ep_dataMC_1351.pdf}
	\caption{The ECal energy over track momentum ratio comparing data and simulation} 
	\label{fig:gains}
\end{center}
\end{figure}
}
The peak position of the distribution indicates the sampling fraction of the ECal, 
the fraction of the incident particle energy measured in the cluster. The width and tails of the distribution 
in data indicates imperfect calibration and noise of the ECal modules. This level of calibration and the 
agreement with simulation was found to be sufficient for the multiple scattering analysis using 
normalized event rates described in Sec.~\ref{sec:mcs}.
